trialStreaks

### 2018-09-06 E1/trialStreaksE1.Rmd
wow i did it

#tidyquant functions search for and key off a date or POSIXct column. 
#So, need to convert trial to that.
lr <- lr %>% mutate(trialDate = as_date(trial))

lags <- lr %>% slice(1:10) %>%
    tidyquant::tq_mutate(
        select     = orientCI,
        mutate_fun = lag.xts,
        k          = 1:4,
        col_rename = col_names
    )
print(lags )

@@

```
Calculate autocorrelation

@@

```{r , fig.height=20, fig.width=5}
lr_autocorr %>%
    ggplot(aes(x = lag, y = cor, color = subject, group = subject)) +
    # Add horizontal line a y=0
    geom_hline(yintercept = 0) +
    # Plot autocorrelations
    geom_point(size = 2) +
    geom_segment(aes(xend = lag, yend = 0), size = 1) +
    # Add cutoffs
    geom_line(aes(y = cutoff_upper), color = "blue", linetype = 2) +
    geom_line(aes(y = cutoff_lower), color = "blue", linetype = 2) +
    # Add facets
    facet_wrap(~ subject, ncol = 3) +
    # Aesthetics
    expand_limits(y = c(-1, 1)) +
    scale_color_tq() +
    theme_tq() +
    labs(
        title = paste0("Tidyverse ACF Plot: Lags ", rlang::expr_text(k)),
        subtitle = "Appears to be a weekly pattern",
        x = "Lags"
    ) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

Print effect size
```{r}
leftBiasesCanonical<- filter(all,dv=="efficacy" & orientation=="Canonical")$leftBias
leftBiasCanonical <- mean( leftBiasesCanonical )
leftBiasesInverted<- filter(all,dv=="efficacy" & orientation=="Inverted")$leftBias
leftBiasInverted<- mean(   leftBiasesInverted  )
leftBiasDiff<- leftBiasCanonical - leftBiasInverted
leftBias_sd <- sd(   leftBiasesCanonical - leftBiasesInverted )
```

>>>>

#tidyquant functions search for and key off a date or POSIXct column. 
#So, need to convert trial to that.
lr <- lr %>% mutate(trialDate = as_date(trial))
lr<- as_tibble(lr)
k <- 1:4
col_names <- paste0("lag_", k)

lags <- lr %>% group_by(subject) %>%
    tidyquant::tq_mutate(
        select     = orientCI,
        mutate_fun = lag.xts,
        k          = 1:4,
        col_rename = col_names
    )
print(lags )

@@

Calculate autocorrelation

@@

```{r , fig.height=5, fig.width=5}
lr_autocorr %>%
    ggplot(aes(x = lag, y = cor, color = subject, group = subject)) +
    # Add horizontal line a y=0
    geom_hline(yintercept = 0) +
    # Plot autocorrelations
    geom_point(size = 2) +
    geom_segment(aes(xend = lag, yend = 0), size = 1) +
    # Add cutoffs
    geom_line(aes(y = cutoff_upper), color = "blue", linetype = 2) +
    geom_line(aes(y = cutoff_lower), color = "blue", linetype = 2) +
    # Add facets
    #facet_wrap(~ subject, ncol = 3) +
    # Aesthetics
    expand_limits(y = c(-.5, .5)) +
    #scale_color_tq() +
    stat_summary(fun.y="mean",geom="line") + #,aes(group=orientation))
    theme_tq() +
    labs(
        title = paste0("autocorrelation: Lags ", rlang::expr_text(k)),
        subtitle = "Appears to have no pattern",
        x = "Lags"
    ) +
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```

Collapse across subjects.

```{r}
lr_autocorr %>% group_by(lag) %>% summarise(cor=mean(cor))
```
